\section{Related Work}
\label{sec:related}

\begin{table*}[t]
\caption{Positioning by task, ownership, privacy object, and released
inference. ``NC'' denotes node classification. Entries describe the formal
scope of each cited work rather than ranking implementations.}
\label{tab:landscape}
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{p{0.12\textwidth}p{0.22\textwidth}p{0.26\textwidth}p{0.31\textwidth}}
\toprule
Work & Ownership / task & Formal privacy object & Released inference contract\\
\midrule
FKGE \cite{peng2021fkge}
& Peer knowledge graphs / KG LP
& PATE-style privacy for generated embeddings
& Cross-domain embeddings; not ordinary-edge adjacency\\
GAP \cite{sajadmanesh2023gap}
& Central ordinary graph / NC
& Add/remove edge- and node-DP aggregation
& Cached noisy channels; no adjacency reread\\
DPLP \cite{ran2024dplp}
& Central ordinary graph / LP
& Edge-private neighborhood/path subgraphs
& Subgraph link predictor; no federated transcript\\
Solitude \cite{lin2022solitude}
& Decentralized adjacency lists / NC
& Local edge- and feature-DP collection
& Server reconstructs a calibrated noisy graph\\
LGA-PGNN \cite{pei2024lga}
& Decentralized local graphs / NC
& Feature-oriented local perturbation
& Class probabilities with attack evaluation\\
PDGL \cite{li2025pdgl}
& Node-held graph records / NC
& Edge-LDP plus cryptographic protocols
& Secure per-node label inference\\
PrivFGL \cite{zhang2025privfgl}
& Cross-silo subgraphs / NC
& Reported node-LDP/CDP transformation
& Federated classifier; no LP score contract\\
PP-HGRL \cite{wang2026pphgrl}
& Client auxiliary relations, server primary graph / recommendation
& Perturbed auxiliary edges and hidden states
& Central recommendation over server-held interactions\\
\method{} (ours)
& Distributed ordinary edges / LP
& Add/remove role-labelled edge DP for full transcript
& Inference-closed scorer plus private utility gate\\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Private graph learning and inference closure}

DP graph learning must control how one edge affects aggregation, optimization,
and inference. GAP perturbs bounded graph aggregations and caches the released
channels, so subsequent prediction does not query the private adjacency
\cite{sajadmanesh2023gap}. This inference-closure principle is part of our
admission contract. DPLP instead studies centralized subgraph-based link
prediction and bounds the dependency induced by neighborhood and path
subgraphs \cite{ran2024dplp}. Our contribution is not a replacement GNN
architecture. It is a private policy for deciding whether any admitted
inference-closed structural branch should be deployed on a target graph.

\subsection{Decentralized and federated private graphs}

Solitude collects decentralized adjacency information with local edge DP
\cite{lin2022solitude}. LGA-PGNN combines local perturbation, graph
augmentation, and attack evaluation \cite{pei2024lga}. PDGL jointly protects
decentralized neighbor lists, features, and labels using DP and cryptographic
components \cite{li2025pdgl}. PrivFGL addresses DP-induced client
heterogeneity in federated node classification
\cite{zhang2025privfgl}. FED-PUB studies personalized learning over distributed
subgraphs without the same edge-DP output contract \cite{baek2023fedpub}, while
Tang and Hu perturb federated GNN training for link prediction under a local
trust model \cite{tang2025privacy}. These systems establish that distributed ownership
and privacy are not novel by themselves. We study a different output contract:
ordinary interaction edges are partitioned across clients; the server-visible
training and certification transcripts are accounted; and the released
candidate-pair scorer cannot reread the private graph.

\subsection{Private link prediction and recommendation}

Federated knowledge-graph embedding has combined DP and link-oriented tasks
under embedding-record adjacency \cite{peng2021fkge}. For ordinary graphs,
DPLP is the closest formal centralized predecessor
\cite{ran2024dplp}. PP-HGRL protects auxiliary heterogeneous relations for
recommendation, while its server owns the primary user-item graph and performs
centralized training \cite{wang2026pphgrl}. CF-DPGNN applies subgraph
sampling and DP-SGD to centralized collaborative filtering
\cite{hu2025cfdpgnn}. Our setting distributes the prediction edges themselves
and evaluates cross-client candidates. More importantly, \method{} addresses
heterogeneous \emph{deployment utility}: it can wrap these or future learners
once their privacy and inference contracts are made compatible.

\subsection{Private hypothesis testing}

The certificate is a private one-sided test over bounded utility records.
Our lower-bound argument uses DP versions of Le Cam's method
\cite{acharya2021private}, while the finite-population analysis uses
sampling-without-replacement concentration
\cite{serfling1974probability}. Unlike generic private model selection,
\method{} releases one frozen binary branch decision and explicitly includes
the certification privacy cost.
