\section{Problem and Privacy Model}
\label{sec:problem}

\subsection{Federated ordinary graph}

Let $V$ be a public node universe, $X$ registered public node descriptors, and
$h:V\rightarrow[K]$ a public home-client map. Client $k$ owns canonical
undirected edges $E_k$ under a public ownership rule; every edge is owned once.
Two federated databases are adjacent when one role-labelled canonical edge is
added to or removed from one client. Features, labels, node existence, and the
home map are outside this edge-DP guarantee.

A public, edge-stable pseudorandom rule assigns records to training $E^T$,
certification $E^C$, or research evaluation $E^Q$. The deployed mechanisms
never read $E^Q$. Our historical benchmark split did not implement an
edge-stable partition, so the R5 accountant deliberately uses sequential
composition rather than claiming disjoint parallel composition.

\subsection{Two inference-closed branches}

The public branch is
\begin{equation}
  s_0(u,v)=F_0(X,u,v;\omega_0),
\end{equation}
where $\omega_0$ is public randomness. A DP trainer releases state
\begin{equation}
  R\leftarrow \cM_T(E^T;X),
\end{equation}
including everything observed by the server. The structural branch is
\begin{equation}
  s_R(u,v)=F_1(R,X,u,v;\omega_1).
\end{equation}
Neither branch may read a private edge, degree, neighborhood, or unprotected
embedding at inference. Hence any number of candidate-pair scores is
post-processing of $R$ and public inputs.

\subsection{Registered utility}

For each certification edge $e=\{u,v\}$, a public seeded map $q$ replaces one
endpoint without graph-dependent rejection. False-negative corruptions are
part of the estimand. For a scorer $s$, define
\begin{equation}
 U_s(e)=\mathbb{1}\{s(e)>s(q(e))\}
 +\tfrac12\mathbb{1}\{s(e)=s(q(e))\}.
\end{equation}
The bounded structural advantage is
\begin{equation}
 d_R(e)=U_{s_R}(e)-U_{s_0}(e)\in[-1,1].
\end{equation}
The target of the R5 theorem is the mean of $d_R$ over one registered finite
holdout population. This pairwise target is related to ranking quality but is
not standard ROC-AUC unless the corruption distribution equals the AUC
negative distribution.

\subsection{Adversary and released outputs}

The primary adversary is an honest-but-curious server that sees every noised
client message, the final DP state, the noised certification statistics, the
binary decision, and all post-processed scores. Ideal secure aggregation is a
secondary trust model in which the server sees only a global aggregate.
Secure aggregation changes utility by reducing aggregate noise; it is not
itself a DP proof.

The deployed output is $(R,\widetilde S,\widetilde n,A)$ and scores from the
selected branch, where $A\in\{0,1\}$ is the activation decision. Publicly
released research metrics on $E^Q$ are evaluation evidence, not outputs of the
deployed DP service.
