\section{\method{}}
\label{sec:method}

\subsection{Private training branch}

\method{} is architecture-agnostic. An admitted trainer must provide its full
RDP curve $\rho_T(\lambda)$ for every registered order $\lambda>1$ and an
inference-closed state $R$. In R5 we instantiate the candidate with a
GAP-style LP adaptation: public descriptors are projected, each client
computes bounded neighbor sums, Gaussian noise is applied per hop, and cached
normalized channels are scored by mean cosine. We call this a
\emph{GAP-style adaptation}, not an official GAP reproduction.

For one hop, changing an undirected edge $\{u,v\}$ changes two bounded node
aggregates. The query has $\ell_2$ sensitivity $\sqrt{2}$. If each visible
client message uses coordinate noise standard deviation $\sigma_T$, the
aggregate contains standard deviation $\sqrt{K}\sigma_T$, although privacy
composes in parallel across unique edge owners. Under ideal secure
aggregation, one aggregate noise draw suffices.

\subsection{Private utility release}

Condition on any realized training release $R=r$. Certification computes
\begin{equation}
 S_r=\sum_{e\in E^C}d_r(e),\qquad n_C=|E^C|.
\end{equation}
One add/remove certification edge changes $(S_r,n_C)$ by at most $(1,1)$ in
absolute coordinates, so
\begin{equation}
 \Delta_2(S_r,n_C)\leq\sqrt{2}.
\end{equation}
Let $\sigma_{\mathrm{abs}}$ denote the absolute coordinate noise standard
deviation. The mechanism releases
\begin{equation}
 (\widetilde S,\widetilde n)
 =(S_r,n_C)+\mathcal N(0,\sigma_{\mathrm{abs}}^2 I_2).
\end{equation}
For visible client messages, independent local noise yields effective
aggregate coordinate deviation
$\nu=(\sum_k\sigma_{\mathrm{abs},k}^2)^{1/2}$; with equal client noise this is
$\sqrt{K}\sigma_{\mathrm{abs}}$. For ideal aggregation,
$\nu=\sigma_{\mathrm{abs}}$.

\subsection{One-sided activation certificate}

Let $\beta_S,\beta_n,\beta_{\rm stat}$ be registered failure allocations and
\begin{equation}
 b_j=\nu\Phi^{-1}(1-\beta_j/2),\quad j\in\{S,n\}.
\end{equation}
Define
\begin{align}
 S_L&=\widetilde S-b_S,\\
 n_L&=\widetilde n-b_n,\qquad n_U=\widetilde n+b_n.
\end{align}
The mechanism abstains unless $S_L>0$, $n_L\geq n_{\min}$, and $n_U>0$.
Otherwise the conservative lower certificate is
\begin{equation}
 L_{\rm pop}
 =\frac{S_L}{n_U}
 -\sqrt{\frac{2\log(1/\beta_{\rm stat})}{n_L}}.
\label{eq:certificate}
\end{equation}
The deployed action is
\begin{equation}
 A=\mathbb{1}\{L_{\rm pop}\geq\gamma\}.
\end{equation}
If $A=1$, the service uses $s_R$; otherwise it uses $s_0$. The threshold
$\gamma$ encodes a material gain, not merely non-inferiority.

\subsection{Privacy accounting}

A Gaussian query with sensitivity $\Delta$ and coordinate standard deviation
$\sigma$ has RDP \cite{mironov2017rdp}
\begin{equation}
 \rho(\lambda)=\frac{\lambda\Delta^2}{2\sigma^2}.
\end{equation}
When the edge-role partition is stable, training and conditional
certification can use adaptive parallel composition. R5 takes the safer
fallback:
\begin{equation}
 \rho_{\rm total}(\lambda)
 =\rho_T(\lambda)+\rho_C(\lambda),
\end{equation}
then converts once,
\begin{equation}
 \eps(\delta)=\min_{\lambda>1}
 \left[
 \rho_{\rm total}(\lambda)
 {}+\frac{\log(1/\delta)}{\lambda-1}
 \right].
\label{eq:rdpconversion}
\end{equation}
Each privacy-grid cell is an alternative deployment. Releasing all cells would
require further composition.
