\section{Discussion and Limitations}
\label{sec:discussion}

\paragraph{What the result establishes.}
\method{} is a deployment policy, not a new graph encoder. It establishes that
a frozen inference-closed structural branch can be privately enabled only
where direct target-domain evidence supports a material pairwise gain. The
main conclusion is certified fallback under heterogeneous utility, not
universal superiority of private graph structure.

\paragraph{Finite versus future populations.}
The no-harm theorem covers the registered sealed holdout population. An
operational system that must generalize to future links needs an additional
sampling assumption, temporal certification window, or repeated privacy
accounting. Shared nodes do not invalidate the finite random-partition proof,
but they can matter for extrapolation beyond that population.

\paragraph{Randomization contract.}
The R5 partition uses a frozen edge-keyed SHA-256 map and its sampling theorem
adopts the registered random-oracle/PRF interpretation. Because the sealed
population was fixed before the salt was frozen and opened, it was not chosen
adaptively against the realized assignment. A deployment in which data
providers can select records after seeing a public salt requires a stronger
protocol: for example, a committed secret PRF key hidden from providers until
the population is fixed, or an auditable random draw after population freeze.
Deterministic SHA-256 alone is not information-theoretic random sampling.

\paragraph{Research metrics and deployment outputs.}
The DP transcript includes training messages, inference-closed state, noised
certificate statistics, the decision, and post-processed score queries.
Unprotected embeddings, graph-backed inference, public test metrics, and
simultaneous release of the diagnostic grid are outside the guarantee.

\paragraph{Candidate dependence.}
Nonvacuity depends on the admitted learner. A stronger candidate can increase
the number of safe activations; a weak one correctly produces fallback. Our
GAP-style candidate is deliberately simple and is not claimed to dominate
existing private graph learners. Certifying learned neural scorers and
temporal target populations is a direct next step.

\paragraph{Trust and client noise.}
Visible independent messages incur aggregate standard deviation proportional
to $\sqrt K$ in this implementation. Ideal secure aggregation removes that
utility penalty but assumes an additional trusted functionality. DP alone
does not hide individual messages from the server.

\paragraph{Statistical multiplicity.}
The confirmatory claim is tied to one preregistered primary cell. The phase
diagram is diagnostic. Deploying multiple candidate branches, thresholds, or
privacy cells on one graph requires privacy composition and statistical
multiplicity control.
