\section{Proof of Training-Only Non-Identifiability}
\label{app:nonidentifiability}

Let $T$ contain every quantity available before target-domain certification,
including public descriptors, the private training transcript, privacy
parameters, and arbitrary training-derived graph statistics. Fix a realization
$T=t$ and two nonempty sets of future comparison records $\mathcal A_+$ and
$\mathcal A_-$ that are not inputs to $T$. Choose the fixed scorers so their
bounded utility difference is $+a$ on $\mathcal A_+$ and $-a$ on
$\mathcal A_-$ for some $a>0$. Let $P_+$ and $P_-$ place target mass on
$\mathcal A_+$ and $\mathcal A_-$, respectively, while keeping all inputs to
$T$ identical.

If a randomized $T$-measurable selector activates with probability $p(t)$,
its expected gain is $p(t)a$ under $P_+$ and $-p(t)a$ under $P_-$. A no-harm
guarantee under $P_-$ forces $p(t)=0$, contradicting nonvacuous activation
under $P_+$. Moreover, relative to a sign oracle, the regrets are
$(1-p)a$ and $pa$; minimax regret is at least $a/2$. Target-domain
certification escapes the construction because its input distributions differ
in the two worlds.

\section{Proof of Transcript Privacy}
\label{app:privacy}

A canonical neighboring edge has one public role. If it belongs to $E^T$,
$E^C$ is identical in the neighboring databases. Conditional certification is
the same Markov kernel applied to the two possible training releases, so
appending it and the decision is post-processing of $\cM_T$. If the edge
belongs to $E^C$, the distribution of $R$ is identical. Uniform conditional
RDP of $\cM_C(\cdot;r)$ remains bounded by $\rho_C(\lambda)$ after integrating
over that common distribution. An $E^Q$ edge affects no deployed mechanism.
Taking the worse of the two affected cases proves \cref{thm:privacy}.

For the certification query $Q_C=(S,n)$, adding or removing one edge changes
one bounded contribution by at most one and the count by one, hence
\begin{equation}
 \Delta_2 Q_C\leq\sqrt{1^2+1^2}=\sqrt2.
\end{equation}
With absolute coordinate noise $\sigma_{\mathrm{abs}}$, its Gaussian RDP is
\begin{equation}
 \rho_C(\lambda)
 =\frac{\lambda\Delta_2^2}{2\sigma_{\mathrm{abs}}^2}.
\end{equation}
The $(\eps,\delta)$ conversion used in every result record is
\begin{equation}
 \eps(\delta)=
 \min_{\lambda\in\Lambda}
 \left\{\rho_{\mathrm{joint}}(\lambda)
       +\frac{\log(1/\delta)}{\lambda-1}\right\}.
\end{equation}
R5 sums the stored training and certification RDP arrays order by order and
then performs this conversion once.

\section{Proof of the Finite-Holdout Certificate}
\label{app:finite}

Condition on $(R,H,n_C)$. The registered edge-keyed Bernoulli hash is
independent across the fixed keys, so conditioning on the count makes $E^C$ a
uniform size-$n_C$ subset of $H$. The values $d_R(e)\in[-1,1]$ are then a fixed
finite population. For
$\widehat\Delta_C=n_C^{-1}\sum_{e\in E^C}d_R(e)$, one-sided
sampling-without-replacement concentration gives
\begin{equation}
 \Pr\{\widehat\Delta_C-\Delta_H\geq t\mid R,H,n_C\}
 \leq
 \exp\!\left(-\frac{n_Ct^2}{2f_N}\right),
\end{equation}
where $f_N=1-(n_C-1)/N\leq1$. R5 uses $f_N=1$ in the decision.

Let $\mathcal G_S$ and $\mathcal G_n$ be the Gaussian events on which the
released sum and count deviate by no more than $b_S$ and $b_n$. On their
intersection, $S_L\leq S$, $n_L\leq n_C\leq n_U$, and, when $S_L>0$,
\begin{equation}
 \frac{S_L}{n_U}\leq\widehat\Delta_C.
\end{equation}
The sampling event implies
\begin{equation}
 \Delta_H\geq\widehat\Delta_C-
 \sqrt{\frac{2\log(1/\beta_{\mathrm{stat}})}{n_C}}
 \geq L_{\mathrm{pop}}.
\end{equation}
A union bound over the two Gaussian events and the sampling event proves
\cref{thm:noharm}. Invalid counts or a nonpositive corrected numerator cause
abstention and cannot create a false activation.

\section{Sufficient Feasibility Boundary}
\label{app:feasibility}

Assume bounded utilities with mean $\Delta$ satisfy
\begin{equation}
 \Pr\{\overline U\leq\Delta-t\}
 \leq\exp\!\left(-\frac{nt^2}{2\chi}\right).
\end{equation}
For an additional power failure $\beta_p$, define
\begin{align}
 a_p(n)&=\sqrt{\frac{2\chi\log(1/\beta_p)}{n}},\\
 a_v(n)&=\sqrt{\frac{2\chi\log(1/\beta_{\mathrm{stat}})}{n}}.
\end{align}
On the sampling and Gaussian good events, the operational certificate is at
least
\begin{equation}
 B(n,\Delta)=
 \frac{n[\Delta-a_p(n)]-2b_S}{n+2b_n}
 -a_v(n-2b_n).
\end{equation}
This expression is valid when $n-2b_n\geq n_{\min}$ and the numerator is
positive. Consequently, $B(n,\Delta)\geq\gamma$ is sufficient for activation
with the registered high probability. Solving for $\Delta$ yields
\begin{align}
 \Delta_{\min}(n)
 =&\,a_p(n)+\frac{2b_S}{n}\\
 &+\frac{n+2b_n}{n}
 \left[\gamma+a_v(n-2b_n)\right].
\end{align}
With no privacy noise, this reduces to
$\gamma+a_p(n)+a_v(n)$.

\section{Necessary Count}
\label{app:lower}

For completeness, consider the registered block-replicated Rademacher hard
pair. Under $H_0$ each independent block is positive with probability
$p_0=(1+\gamma)/2$; under $H_1$ it is positive with probability
$p_1=(1+\gamma+\alpha)/2$. There are $n/\chi$ independent blocks and each is
replicated $\chi$ times. Classical Le Cam and Pinsker inequalities imply
\begin{equation}
 n\geq
 \frac{2\chi(1-2\eta)^2}
      {D_{\mathrm{KL}}(\operatorname{Ber}(p_0)
       \Vert\operatorname{Ber}(p_1))}.
\end{equation}

For the privacy term, convert add/remove $(\eps,\delta)$-DP to replacement
privacy with $\eps_r=2\eps$ and
$\delta_r=(1+e^\eps)\delta$. Let $D_\star$ be the smallest nonnegative
solution of
\begin{equation}
 0.9e^{-10\eps_rD}-10D\delta_r\leq2\eta.
\end{equation}
Under maximal coupling the expected replacement Hamming distance is
$n\alpha/2$. The approximate-DP Le Cam bound in
\cite{acharya2021private} therefore requires
\begin{equation}
 n\geq\frac{2D_\star}{\alpha}.
\end{equation}
For pure DP, this gives
$n\geq\log(0.9/(2\eta))/(10\eps\alpha)$. Since
\begin{equation}
D_{\mathrm{KL}}(\operatorname{Ber}(p_0)
\Vert\operatorname{Ber}(p_1))
=\frac{\alpha^2}{2(1-\gamma^2)}+O(\alpha^3),
\end{equation}
the principal necessary rate is
$\Omega(\chi/\alpha^2+1/(\eps\alpha))$.

\section{Reproducibility and Claim Boundaries}

The accompanying artifact contains the frozen primary configuration, immutable
raw outcomes, summary, authoritative one-time access record, and independent
audit. The runner is fixed at commit \texttt{dcdbf2e}. Every result stores its
full RDP array and distinguishes the confirmatory cell from the diagnostic
grid.

The following are intentionally not claimed: a confidence interval for
ROC-AUC, temporal or cross-domain no-harm, official reproduction or universal
superiority of GAP, simultaneous private release of the phase grid, or privacy
for an inference path that rereads an unreleased private graph.
